Contribution Title\thanks{Supported by organization x.}

### 2019-12-17 sections/evaluation.tex
summarize DL experiment observation

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.7cm} | m{4cm}| m{2cm} | m{2.75cm} |  } 
\hline
Solver & \# solved (SAT, UNSAT) & PAR-2 & Avg clause Size \\ 
\hline
SAT 2017 Winner & & & \\
$\MapleSeven$ & 232 (135, 97) & 4755.96 & 61.9  \\ 
\hline
$\MapleSeven$-i-pure & \textbf{244 (146, 98)} +12 & \textbf{4504.18} & 43.76 \\
\hline
$\MapleSeven$-i-min & 240 (144, 96) +8 & 4601.25 & \textbf{36.97} \\ 
\hline
$\MapleSeven$-i-greedy & 237 (140, 97) +5 & 4678.434 & 43.62 \\ 
\hline
$\MapleSeven$-i-inclusive & 234 (137, 97) +2 & 4718.03 & 37.96 \\
\hline
\hline
SAT 2018 Winner & & & \\
$\MapleEightShort$ & 236 (138, 98) & 4671.81 & 61.69 \\
\hline
$\MapleEightShort$-i-pure & \textbf{241} (\textbf{142, 99}) +5 & \textbf{4598.18} & 44.19 \\
\hline
$\MapleEightShort$-i-min & 236 (141, 95) +0 & 4683.92 & 38.05 \\ 
\hline
$\MapleEightShort$-i-greedy & 240 (141, \textbf{99}) +4 & 4626.99 & 41.16 \\
\hline
$\MapleEightShort$-i-inclusive & 240 (\textbf{142}, 98) +4 & 4602.13 & \textbf{37.52} \\
\hline
\hline
SAT 2019 Winner & & & \\
$\MapleNineShort$ & 238 (140, \textbf{98}) & 4531.24 & 60.91 \\
\hline
$\MapleNineShort$-i-pure & 238 (140, 98) +0 & 4519.08 &  43.32\\
\hline
$\MapleNineShort$-i-min & 244 (148, 96) +6 & \textbf{4409.88} & \textbf{37.43} \\
\hline
$\MapleNineShort$-i-greedy & 243 (146, 97) + 5 & 4476.73 & 40.65 \\
\hline
$\MapleNineShort$-i-inclusive & \textbf{245} (\textbf{150}, 95) +7 & 4425.99 & 37.60 \\
\hline
\hline
SAT 2019 Competitor & & &\\
$\expSATShort$ & 237 (137, 100)  & 4628.96 & 63.19 \\
\hline
$\expSATShort$-i-pure & 235 (136, 99) -2  & 4668.96 & 48.26 \\
\hline
$\expSATShort$-i-min & 241 (143, 98) +4 & 4524.28 & 46.29 \\ 
\hline
$\expSATShort$-i-greedy & 244 (143, \textbf{101}) +7 & \textbf{4460.92} & 47.25 \\
\hline
$\expSATShort$-i-inclusive & \textbf{245} (\textbf{146}, 99) +8 & 4475.76 & \textbf{45.33} \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of 1-UIP, $\IUIPPURE$. $\IUIPMIN$, $\IUIPGreedy$ and $\IUIPActive$ on SAT2019 race main track.}
\label{fig:t5}
\end{figure}

@@

$\IUIP$ learning schemes showed significant improvement for $\MapleNineShort$. Three out of four configurations improved solved instances by 6, 5 and 7 instances, respectively. $\MapleNineShort$ uses duplicate learning (DL) to prioritize clauses that are learned multiple times. $\IUIP$ and DL didn't synergies well possibly because different 1-UIP clause can be reduced to the same i-UIP clause through $\IUIP$ learning; therefore, DL could encounter too many duplicate i-uip clauses to correctly prioritize the important clauses. \nf{should I run some experiment to validate my guess?, if the guess is valid, should I adjust DL settings to make it compatible with $\IUIP$}

We observed significant improvement of $\IUIP$ for $\MapleSeven$, three out of four configurations of $\IUIP$ significantly outperformed 1-UIP learning by 4, 7 and 8 more instances, respectively, while producing smaller clauses. We expect all three configurations of $\IUIP$ to solve the similar amount of instances with close PAR-2 scores because the additional random walk exploration allows the learning schemes to partially sidestep the activity problem; hence, the learning adjustment for variable activities should have less impact on the solver's performance. However, we observed that both $\IUIPGreedy$ and $\IUIPActive$ outperformed the default i-UIP learning scheme. One possible explanation is that $\IUIPGreedy$ and $\IUIPActive$ schemes could easily overcompensate variable activities for i-UIP clauses, and $\expSATShort$'s random walk exploration could use future search information to mitigate the negative effects of our overcompensation.

>>>>

\begin{figure} 
\begin{center}
\begin{tabular}{ | m{3.7cm} | m{4cm}| m{2cm} | m{2.75cm} |  } 
\hline
Solver & \# solved (SAT, UNSAT) & PAR-2 & Avg clause Size \\ 
\hline
SAT 2017 Winner & & & \\
$\MapleSeven$ & 232 (135, 97) & 4755.96 & 61.9  \\ 
\hline
$\MapleSeven$-i-pure & \textbf{244 (146, 98)} +12 & \textbf{4504.18} & 43.76 \\
\hline
$\MapleSeven$-i-min & 240 (144, 96) +8 & 4601.25 & \textbf{36.97} \\ 
\hline
$\MapleSeven$-i-greedy & 237 (140, 97) +5 & 4678.434 & 43.62 \\ 
\hline
$\MapleSeven$-i-inclusive & 234 (137, 97) +2 & 4718.03 & 37.96 \\
\hline
\hline
SAT 2018 Winner & & & \\
$\MapleEightShort$ & 236 (138, 98) & 4671.81 & 61.69 \\
\hline
$\MapleEightShort$-i-pure & \textbf{241} (\textbf{142, 99}) +5 & \textbf{4598.18} & 44.19 \\
\hline
$\MapleEightShort$-i-min & 236 (141, 95) +0 & 4683.92 & 38.05 \\ 
\hline
$\MapleEightShort$-i-greedy & 240 (141, \textbf{99}) +4 & 4626.99 & 41.16 \\
\hline
$\MapleEightShort$-i-inclusive & 240 (\textbf{142}, 98) +4 & 4602.13 & \textbf{37.52} \\
\hline
\hline
SAT 2019 Winner & & & \\
$\MapleNineShort$ & 238 (140, \textbf{98}) & 4531.24 & 60.91 \\
\hline
$\MapleNineShort$-i-pure & 238 (140, \textbf{98}) +0 & 4519.08 &  43.32\\
\hline
$\MapleNineShort$-i-min & 244 (148, 96) +6 & \textbf{4409.88} & \textbf{37.43} \\
\hline
$\MapleNineShort$-i-greedy & 243 (146, 97) + 5 & 4476.73 & 40.65 \\
\hline
$\MapleNineShort$-i-inclusive & \textbf{245} (\textbf{150}, 95) +7 & 4425.99 & 37.60 \\
\hline
\hline
SAT 2019 Competitor & & &\\
$\expSATShort$ & 237 (137, 100)  & 4628.96 & 63.19 \\
\hline
$\expSATShort$-i-pure & 235 (136, 99) -2  & 4668.96 & 48.26 \\
\hline
$\expSATShort$-i-min & 241 (143, 98) +4 & 4524.28 & 46.29 \\ 
\hline
$\expSATShort$-i-greedy & 244 (143, \textbf{101}) +7 & \textbf{4460.92} & 47.25 \\
\hline
$\expSATShort$-i-inclusive & \textbf{245} (\textbf{146}, 99) +8 & 4475.76 & \textbf{45.33} \\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of 1-UIP, $\IUIPPURE$. $\IUIPMIN$, $\IUIPGreedy$ and $\IUIPActive$ on SAT2019 race main track.}
\label{fig:t5}
\end{figure}

@@

$\IUIP$ learning schemes showed significant improvement for $\MapleNineShort$. Three out of four configurations improved solved instances by 6, 5 and 7 instances, respectively. $\MapleNineShort$ uses duplicate learning (DL) to prioritize clauses that are learned multiple times. $\IUIP$ and DL didn't synergies well possibly because i-uip clauses are less likely to be duplicated. We observed that $\IUIPMIN$ ,in average, added 12\% less duplicated clauses into the core clause database. One possible explanation is that the conflict blocked by a single 1-uip clauses can be alternatively blocked by one of many i-uip clauses. Therefore, the same 1-uip clause can be reduced to different i-uip clauses depending on the solver's assertion trail.

We observed significant improvement of $\IUIP$ for $\expSATShort$, three out of four configurations of $\IUIP$ significantly outperformed 1-UIP learning by 4, 7 and 8 more instances, respectively, while producing smaller clauses. We expect all three configurations of $\IUIP$ to solve the similar amount of instances with close PAR-2 scores because the additional random walk exploration allows the learning schemes to partially sidestep the activity problem; hence, the learning adjustment for variable activities should have less impact on the solver's performance. However, we observed that both $\IUIPGreedy$ and $\IUIPActive$ outperformed the default i-UIP learning scheme. One possible explanation is that $\IUIPGreedy$ and $\IUIPActive$ schemes could easily overcompensate variable activities for i-UIP clauses, and $\expSATShort$'s random walk exploration could use future search information to mitigate the negative effects of our overcompensation.
